---
date: "March 22, 2005"
title: "Performance report"
author: Andrzej Kopec (andrzej.kopec@brenntag.pl)
geometry: left=1cm,right=1cm,top=0.5cm,bottom=1cm, a4paper
documentclass: report
classoption: landscape
header-includes:
- \AtBeginDocument{\let\maketitle\relax}
 # % Allows me to use and print accented characters (document is in Spanish)
- \usepackage[T1]{fontenc}
- \usepackage[utf8]{inputenc}
 # % It allows me to place the tables or images where I want, whether there is space or not
- \usepackage{float}
 # % It has several commands to have more control over the tables (at least I use it for this)
- \usepackage{array}
 # % For custom headers and footers
- \usepackage{fancyhdr}
#  % This line allows me to manipulate images within latex
- \usepackage{graphicx}
 # % This package has several uses, for this document I used it to manage hyperlinks and introduce metadata to the document
 # % These lines define the font that I want to use in the document
- \usepackage{caption} #  aby schować numery tabel a zostawić tylko opis
- \usepackage{helvet}
- \renewcommand{\familydefault}{\sfdefault}
- \usepackage{datetime}
- \usepackage{numprint}
- \usepackage{parskip}
- \usepackage{siunitx}
- \usepackage{pdflscape}
- \usepackage{svg}
- \usepackage{xstring}
- \usepackage{fontspec}
- \usepackage{fontsize}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{titlesec}
- \usepackage[titletoc]{appendix}
- \usepackage{wrapfig}
- \usepackage{tgheros}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage[singlelinecheck=false]{caption}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{lipsum}  
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{afterpage}
#- \usepackage{helvet}
#- \renewcommand\familydefault{\sfdefault}
#- \usepackage[polish]{babel}
#- \setmainfont{72}
- \usepackage{setspace}
- \usepackage{amsmath, booktabs, caption, longtable}
#- \setlength{\headheight}{13pt}
- \pagestyle{fancy}
- \lfoot{\fontsize{6pt}{11pt}\selectfont STRICLY CONFIDENTIAL. SHARING WITH UNAUTHORIZED PERSONS IS NOT PERMITTED}
- \rfoot{\fontsize{6pt}{11pt}\selectfont {\thepage}}
- \rhead{\includegraphics[width=35mm]{BrenntagPurple.png}\vspace{-8mm}}
- \renewcommand{\headrulewidth}{0pt}
- \cfoot{}
- \chead{}
- \lhead{}
# - \rhead{}   żeby nic się nie pojawiało po prawej stronie nagłówka strony
# - \setcounter{secnumdepth}{0} #gubią się odniesienia 
- \usepackage[export]{adjustbox}
- \setlength\parindent{24pt}
- \renewcommand{\contentsname}{Table of contents} 
- \usepackage{hyperref} #ten pakiet musi być ładowany  na końcu
# - \makeatletter
# - \renewcommand{\@seccntformat}[0]{}
# - \makeatother



output:
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes

---


\titleformat{\chapter}[display]
  {\normalfont\bfseries}{}{0pt}{\Huge}
  
\thispagestyle{empty}
\definecolor{Brenntag}{RGB}{255, 255, 255}
\pagecolor{Brenntag}\afterpage{\nopagecolor}
\fontfamily{qhv}
\fontsize{12}{23}
<!-- \fontsize{12}{22} -->

\selectfont
\captionsetup[table]{labelformat=empty}

<!-- \vspace{10mm} -->


<!-- \addtocontents{toc}{\protect\newpage} -->
<!-- <!-- \noindent\makebox[\linewidth]{\rule{\paperwidth}{0.8pt}} --> 

<!-- <!-- \noindent\rule{25cm}{0.4pt} --> 

\newgeometry{top=5.5cm,bottom=0.8cm,right=9cm,left=1.5cm}

<!--\textbf{\textcolor{white}{\HUGE BRENNTAG CEE PERFORMANCE REPORT}}--> 
\textbf{\textcolor{black}{\LARGE BRENNTAG CEE PERFORMANCE REPORT}}

\vspace{-4mm} 
\includegraphics[width=750pt]{liniaBR.png} 

\vspace{-2mm}
\textbf{\textcolor{black}{\small `r paste(MiesiacAnalizyTekst,RokAnalizy,sep=" ")`}}





<!-- \makebox[\textheight]{\includegraphics[width=\textheight]{BREN2.png}} -->



```{python, echo=FALSE, warnings=FALSE}
# 
# import pandas as pd
# import plotly.express as px
# import numpy as np
# import plotly.io as pio

# # import data from xlsx file
# df = pd.read_excel('C:/Users/plakopec/OneDrive - brenntagceen/PROJEKTY/PerformenceRaportAnalizy/PerformanceRaport/sources/Dane_do_mapy_drzewaZS.xlsx', sheet_name='Sheet 1')
# 
# my_colors = [
#     # [0.0, '#FF0000'], # ciemny zielony
#     # [0.5, '#FFFFFF'], # biały
#     # [1.0, '#064F06']  # czerwony
#     [0.0, '#B714CF'], # ciemny zielony
#     [0.5, '#FFFFFF'], # biały
#     [1.0, '#0C72ED']  # czerwony
# ]
# 
# colorscale = my_colors    
# 
# fig = px.treemap(df, path=[px.Constant("ZMIANA WOLUMENU I-III W PORÓWNANIU DO 2022"),'ZMIANA WOLUMENU','PM','Hierarchia3'], values='Wolumen [MT]',
#         color='Zmiana marży YTD', 
#         color_continuous_scale=colorscale,
#         color_continuous_midpoint=0)
#                  
# fig.update_layout(margin = dict(t=10, l=5, r=5, b=5),showlegend=False)
# fig.update_traces(marker = dict(cornerradius=4))
# 
# 
# 
# fig.show()
# pio.write_html(fig, file='C:/Users/plakopec/OneDrive - brenntagceen/PROJEKTY/PerformenceRaportAnalizy/PerformanceRaport/output/produkty.html', auto_open=False)
# 


```


\newpage

\newgeometry{top=1.5cm,bottom=0.8cm,right=4cm,left=1.5cm}


\thispagestyle{empty}



\footnotesize \tableofcontents

\thispagestyle{empty}

\newpage
\newgeometry{top=1.5cm,bottom=1cm,right=4cm,left=1.5cm}



\thispagestyle{empty}
# CEE TOTAL RESULT
\vspace{-1.7cm}
\rule{730pt}{1.5pt}


\thispagestyle{empty}





\newpage
\newgeometry{top=1.5cm,bottom=1.3cm,right=0.8cm,left=0.8cm}
```{r setup, include=FALSE,cache=FALSE}
knitr::opts_chunk$set(cache = FALSE,echo = FALSE,warning = FALSE,error = FALSE,comment = FALSE)
```

\npthousandsep{\,}

## TOTAL RESULT (`r MiesiacAnalizyTekst`)

<!-- \vspace{-4mm} -->

<!-- \leftskip 36pt  \scriptsize 3rd party + intercompany -->
<!-- \vspace{-1mm} -->
<!-- \leftskip 0pt -->

```{r MAINTOTAL, echo=FALSE,warning=FALSE}
Tablica_X             <- CreateTable(MainTotal,nazwa_tabeli = "MainTotal")
#browser()
Tabela                <- Tablica_X[[1]]
Wiersze_do_boldowania <- Tablica_X[[2]]

Quant         <- Tabela[nrow(Tabela),2]
Quant_PRV     <- Tabela[nrow(Tabela),3]
GrossProf     <- Tabela[nrow(Tabela),6]
GrossProf_PRV <- Tabela[nrow(Tabela),7]
Turnov        <- Tabela[nrow(Tabela),10]
Turnov_PRV    <- Tabela[nrow(Tabela),11]
GPMT          <- Tabela[nrow(Tabela),14]
GPMT_PRV      <- Tabela[nrow(Tabela),15]


Tabela[,2:17] <- lapply(Tabela[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

zen <-kbl(Tabela,  booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
row_spec(Wiersze_do_boldowania, bold = T)  %>% #, background = "#E3E3E3") %>%       WYBOLDOWANIE POWINNO BYĆ SPARAMETRYZOWANE
row_spec(nrow(Tabela), bold = T ,background = "#E3E3E3") 


zen <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",zen)

zen


```

## TOTAL RESULT (YTD)

```{r MAINTOTALYTD, echo=FALSE}
Tablica_X              <- CreateTable(MainTotalYTD,nazwa_tabeli = "MainTotalYTD")
Tabela1                <- Tablica_X[[1]]
Wiersze_do_boldowania1 <- Tablica_X[[2]]

Quant_YTD         <- Tabela1[nrow(Tabela1),2]
Quant_PRV_YTD     <- Tabela1[nrow(Tabela1),3]
GrossProf_YTD     <- Tabela1[nrow(Tabela1),6]
GrossProf_PRV_YTD <- Tabela1[nrow(Tabela1),7]
Turnov_YTD        <- Tabela1[nrow(Tabela1),10]
Turnov_PRV_YTD    <- Tabela1[nrow(Tabela1),11]
GPMT_YTD          <- Tabela1[nrow(Tabela1),14]
GPMT_PRV_YTD      <- Tabela1[nrow(Tabela1),15]

Tabela        <- as.data.frame(Tabela)

Tabela1[,2:17] <- lapply(Tabela1[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

#Tabela1[Tabela1$SubRegion=="Poland",4] <-paste("\\underline{", Tabela1[Tabela1$SubRegion=="Poland",4], "}",sep="")
#Tabela1[Tabela1$SubRegion=="Poland",4] <-paste0("\\href{", "produkty.html",Kraj1, "}","{", Tabela1[Tabela1$SubRegion=="Poland",4], "}")



zen2<-kbl(Tabela1, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
row_spec(Wiersze_do_boldowania1, bold = T)  %>%   # ,background = "#E3E3E3"
 #, background = "#E3E3E3") %>%       WYBOLDOWANIE SPARAMETRYZOWANE
row_spec(nrow(Tabela), bold = T, background = "#E3E3E3")

zen2<-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",zen2)

source(here::here("moduly","zbuduj_baze2.R"))

zen2

```

\newpage

## TOTAL RESULT. CHARTS.

```{r Wykres, fig.height=6.7,fig.width=szerokoscWykresuTotalResult}





WykresZZ

```

\newpage

## COUNTRIES BY DIVISIONS (`r MiesiacAnalizyTekst`)


```{r COUNTRIESBYDIVISIONy}

Tablica_X               <- CreateTable(CountriesByDivision,nazwa_tabeli ="CountriesByDivision",pomocnicza = PHOSPHATESFAS2a)
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
BoldowaniePomocnicze    <- Tablica_X[[4]]
TotalWiersz             <- max(podkreslanie)+1

Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(TotalWiersz, bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE) %>% 
  row_spec(podkreslanie, bold = T, background = "#C9C9C9") %>%
  row_spec(BoldowaniePomocnicze, bold = T)#,background = "#E3E3E3")



klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```


\newpage

## COUNTRIES BY DIVISIONS (YTD)


<!-- \scriptsize 3rd party + intercompany -->
<!-- \vspace{-2mm} -->


```{r COUNTRIESBYDIVISION}

Tablica_X               <- CreateTable(CountriesByDivision_YTD,nazwa_tabeli ="CountriesByDivision_YTD",pomocnicza = PHOSPHATESFAS_YTD2a)
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
BoldowaniePomocnicze    <- Tablica_X[[4]]
TotalWiersz             <- max(podkreslanie)+1



Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(TotalWiersz, bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE) %>% 
  row_spec(podkreslanie, bold = T, background = "#C9C9C9") %>%
  row_spec(BoldowaniePomocnicze, bold = T)#,background = "#E3E3E3")

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```

\newpage

## COUNTRIES BY SALES PARTY (`r MiesiacAnalizyTekst`)


```{r SALES_MAIN, echo=FALSE}

Tablica_X             <- CreateTable(SALES_MAIN,nazwa_tabeli = "SALES_MAIN")
Tabela39                <- Tablica_X[[1]]
Wiersze_do_boldowania39 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]

Tabela39[,2:17] <- lapply(Tabela39[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon42<-kbl(Tabela39, longtable=TRUE,booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]])-3, bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania39, bold = T, hline_after=TRUE)#,background = "#E3E3E3") 
  

klon42 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon42)
klon42

```

\newpage

## COUNTRIES BY SALES PARTY (YTD)



```{r SALES_MAIN_YTD, echo=FALSE}

Tablica_X               <- CreateTable(SALES_MAIN_YTD,nazwa_tabeli = "SALES_MAIN_YTD")
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43<-kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]])-3, bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE)

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```




\newpage
## COUNTRIES BY INDUSTRIES (`r MiesiacAnalizyTekst`)
```{r COUNTRIESBYINDUSTRIESy}

Tablica_X               <- CreateTable(CountriesByIndustries)
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]

Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE)

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```


\newpage
## COUNTRIES BY INDUSTRIES (YTD)
```{r COUNTRIESBYINDUSTRIES}

Tablica_X               <- CreateTable(CountriesByIndustries_YTD)
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]

Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T, hline_after=TRUE)

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```



\newpage

## DIVISIONS (`r MiesiacAnalizyTekst`)


```{r MAIN_ISP, echo=FALSE}

Tablica_X                <- CreateTable(ICCPM_DATA,nazwa_tabeli ="ICCPM_DATA",pomocnicza = PHOSPHATESFAS)
Tabela10                 <- Tablica_X[[1]]
Wiersze_do_boldowania10  <- Tablica_X[[2]]


Tabela10[,2:17] <- lapply(Tabela10[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon8 <-kbl(Tabela10, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
row_spec(nrow(Tablica_X[[1]])-2, bold = T,background = TloTotalTotal) %>% 
row_spec(Wiersze_do_boldowania10,hline_after = TRUE, bold = T)#,background = "#E3E3E3") 

klon8 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon8)
klon8

```


\newpage

## DIVISIONS (YTD)


```{r MAIN_ISPY, echo=FALSE}

Tablica_X             <- CreateTable(ICCPM_DATAY ,nazwa_tabeli ="ICCPM_DATAY",pomocnicza = PHOSPHATESFAS_YTD )
Tabela11                <- Tablica_X[[1]]
Wiersze_do_boldowania11 <- Tablica_X[[2]]

Tabela11[,2:17] <- lapply(Tabela11[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon9 <-kbl(Tabela11, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
row_spec(nrow(Tablica_X[[1]])-2, bold = T,background = TloTotalTotal) %>% 
row_spec(Wiersze_do_boldowania11 , hline_after = TRUE, bold = T)#,background = "#E3E3E3") 

klon9 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon9)
klon9

```




\newpage
## DIVISIONS BY COUNTRY (`r MiesiacAnalizyTekst`)
```{r TotalDivisionSalesCountry}

Tablica_X               <- CreateTable(DivisionsByCountry,nazwa_tabeli ="DivisionsByCountry",pomocnicza = PHOSPHATESFAS2 )
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
BoldowaniePomocnicze    <- Tablica_X[[4]]
TotalWiersz             <- max(podkreslanie)+1
Tabela40[,2:17]         <- lapply(Tabela40[,2:17], function(x) {
                                cell_spec(x,
                                color = ifelse(x<0,"#C815E0","black"))
                                })

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(TotalWiersz, bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE) %>% 
row_spec(podkreslanie, bold = T, background = "#C9C9C9") %>% 
row_spec(BoldowaniePomocnicze, bold = T, hline_after = TRUE)#,background = "#C9C9C9")

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```


\newpage
## DIVISIONS BY COUNTRY (YTD)
```{r TotalDivisionSalesCountryYTD}

Tablica_X               <- CreateTable(DivisionsByCountry_YTD,nazwa_tabeli ="DivisionsByCountry_YTD",pomocnicza = PHOSPHATESFAS_YTD2 )
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
BoldowaniePomocnicze    <- Tablica_X[[4]]
TotalWiersz             <- max(podkreslanie)+1

Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(TotalWiersz, bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE) %>% 
row_spec(podkreslanie, bold = T,background = "#C9C9C9") %>% #, background = "#C9C9C9") %>% 
row_spec(BoldowaniePomocnicze, bold = T,hline_after = TRUE)#,background = "#E3E3E3")
klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```


\newpage

## DIVISIONS BY SALES PARTY (`r MiesiacAnalizyTekst`)

```{r TotalDivisionSalesParty}

Tablica_X               <- CreateTable(TotalDivisionSalesParty,nazwa_tabeli = "TotalDivisionSalesParty")
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
BoldowaniePomocnicze    <- Tablica_X[[4]]
TotalWiersz             <- max(podkreslanie)+1
Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(TotalWiersz, bold = T,background = TloTotalTotal) %>%  
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE) %>% 
row_spec(podkreslanie, bold = T, background = "#C9C9C9") %>% 
row_spec(BoldowaniePomocnicze, bold = T,hline_after=TRUE)#,background = "#C9C9C9")
 

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```


\newpage

## DIVISIONS BY SALES PARTY (YTD)

```{r TotalDivisionSalesPartyYTD}

Tablica_X               <- CreateTable(TotalDivisionSalesParty_YTD,nazwa_tabeli ="TotalDivisionSalesParty_YTD")
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
BoldowaniePomocnicze    <- Tablica_X[[4]]
TotalWiersz             <- max(podkreslanie)+1
Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(TotalWiersz, bold = T,background = TloTotalTotal) %>%
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40,hline_after=TRUE, bold = T) %>% 
row_spec(podkreslanie, bold = T, background = "#C9C9C9") %>% 
row_spec(BoldowaniePomocnicze, bold = T,hline_after=TRUE)#,background = "#C9C9C9")

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```




\newpage
## INDUSTRIES BY COUNTRY (`r MiesiacAnalizyTekst`)
```{r TotalIndustrySalesCountry}

Tablica_X               <- CreateTable(IndustryByCountry)
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]

Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE)

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```

\newpage
## INDUSTRIES BY COUNTRY (YTD)
```{r TotalIndustryCountryYTD}

Tablica_X               <- CreateTable(IndustryByCountry_YTD)
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]

Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE)

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```


\newpage

## INDUSTRIES AND MATERIAL TYPES  (`r MiesiacAnalizyTekst`)

ES-essentials and SP-specialties based on local classification - dependent ONLY on product parameters&local decisions, not connected with customer/industry

```{r MAIN_ESSP_T, echo=FALSE}

Tablica_X             <- CreateTable(MAIN_ESSP_T,nazwa_tabeli ="MAIN_ESSP_T")
Tabela8                <- Tablica_X[[1]]
Wiersze_do_boldowania8 <- Tablica_X[[2]]

Tabela8[,2:17] <- lapply(Tabela8[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon6<-kbl(Tabela8, longtable=T, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
row_spec(Wiersze_do_boldowania8, bold = T, hline_after=TRUE) 

klon6<-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon6)
#klon12 <-str_replace_all(klon6,fixed("{\\linewidth}{!}"),"{0.6}")

klon6

```


\newpage

## INDUSTRIES AND MATERIAL TYPES (YTD)


```{r MAIN_ESSP_TY, echo=FALSE}

Tablica_X             <- CreateTable(MAIN_ESSP_TY,nazwa_tabeli ="MAIN_ESSP_TY" )
Tabela9                <- Tablica_X[[1]]
Wiersze_do_boldowania9 <- Tablica_X[[2]]

Tabela9[,2:17] <- lapply(Tabela9[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon7<-kbl(Tabela9, longtable=T, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
row_spec(Wiersze_do_boldowania9, bold = T, hline_after=TRUE) #,background = "#E3E3E3") 

klon7<-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon7)
klon7

```

\newpage

## EUROPEAN INDUSTRIES (`r MiesiacAnalizyTekst`)

```{r MAIN_Eur, echo=FALSE}

Tablica_X              <- CreateTable(MAIN_EUR_IND)
Tabela6                <- Tablica_X[[1]]
Wiersze_do_boldowania6 <- Tablica_X[[2]]


Tabela6[,2:17] <- lapply(Tabela6[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon4<-kbl(Tabela6, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
row_spec(Wiersze_do_boldowania6, bold = T,hline_after = TRUE) #,background = "#E3E3E3"

klon4<-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon4)
klon4


```

\newpage

## EUROPEAN INDUSTRIES (YTD)

```{r MAIN_Eur_Y, echo=FALSE}

Tablica_X             <- CreateTable(MAIN_EUR_IND_Y)
Tabela7                <- Tablica_X[[1]]
Wiersze_do_boldowania7 <- Tablica_X[[2]]

Tabela7[,2:17] <- lapply(Tabela7[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon5<-kbl(Tabela7, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
row_spec(Wiersze_do_boldowania7, bold = T,hline_after = TRUE) #background = "#E3E3E3"

klon5<-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon5)
klon5


```


\newpage
<!-- \newgeometry{top=1.4cm,bottom=1.3cm,right=0.7cm,left=0.7cm} -->
## ES|SP MATERIAL TYPES BY COUNTRY (`r MiesiacAnalizyTekst`)


```{r MAINTOTALESSP, echo=FALSE}

Tablica_X             <- CreateTable(MAIN_ESSP,nazwa_tabeli = "MAIN_ESSP")
Tabela2                <- Tablica_X[[1]]
Wiersze_do_boldowania2 <- Tablica_X[[2]]


Tabela2[,2:17] <- lapply(Tabela2[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})


klon0<-kbl(Tabela2, longtable=TRUE,booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","repeat_header")) %>% 
add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(nrow(Tablica_X[[1]])-3, bold = T,background = "#E3E3E3") %>% 
# row_spec(Wiersze_do_boldowania2, bold = T,background = "#E3E3E3") 
row_spec(Wiersze_do_boldowania2, bold = T,hline_after=TRUE)   
  

klon0<-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon0)
klon0

```



\newpage

## ES|SP MATERIAL TYPES BY COUNTRY (YTD)

```{r MAINTOTALESSPYTD, echo=FALSE}

Tablica_X              <- CreateTable(MAIN_ESSP_YTD, nazwa_tabeli = "MAIN_ESSP_YTD")
Tabela3                <- Tablica_X[[1]]
Wiersze_do_boldowania3 <- Tablica_X[[2]]

Tabela3[,2:17] <- lapply(Tabela3[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})


klon<-kbl(Tabela3, longtable=TRUE, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(nrow(Tablica_X[[1]])-3, bold = T,background = "#E3E3E3") %>% 
row_spec(Wiersze_do_boldowania3, bold = T,hline_after=TRUE) #row_spec(Wiersze_do_boldowania3, bold = T,background = "#E3E3E3") 

klon<-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon)
klon


```


\newpage

<!-- \newgeometry{top=1.5cm,bottom=1.3cm,right=0.8cm,left=0.8cm} -->
## WAREHOUSE|DIRECT BY COUNTRY  (`r MiesiacAnalizyTekst`)

\vspace{-1mm}
```{r MAIN_WhDir_MTH, echo=FALSE}

Tablica_X             <- CreateTable(MAIN_WhDir_MTH,nazwa_tabeli = "MAIN_WhDir_MTH")
Tabela4                <- Tablica_X[[1]]
Wiersze_do_boldowania4 <- Tablica_X[[2]]
TotalWiersz           <- max(Wiersze_do_boldowania4)+1
Tabela4[,2:17] <- lapply(Tabela4[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon2<-kbl(Tabela4, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(TotalWiersz, bold = T,background = TloTotalTotal)  %>% 
# row_spec(Wiersze_do_boldowania4, bold = T,background = "#E3E3E3") 
row_spec(Wiersze_do_boldowania4, bold = T,hline_after = TRUE) 

klon2<-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon2)
klon2

```
 
\newpage

## WAREHOUSE|DIRECT BY COUNTRY (YTD)

\vspace{-1mm}
```{r MAIN_WhDir_YTD, echo=FALSE}

Tablica_X              <- CreateTable(MAIN_WhDir_YTD,nazwa_tabeli = "MAIN_WhDir_YTD")
Tabela5                <- Tablica_X[[1]]
Wiersze_do_boldowania5 <- Tablica_X[[2]]
TotalWiersz           <- max(Wiersze_do_boldowania5)+1

Tabela5[,2:17] <- lapply(Tabela5[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon3<-kbl(Tabela5, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania5, bold = T, hline_after = TRUE) %>%  #row_spec(Wiersze_do_boldowania5, bold = T,background = "#E3E3E3") %>% 
row_spec(TotalWiersz, bold = T,background = TloTotalTotal) 

klon3<-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon3)
klon3

```
 

\newpage

## CEEKAT/EKAT BY COUNTRY (`r MiesiacAnalizyTekst`)


```{r EKAT, echo=FALSE}

Tablica_X             <- CreateTable(EKAT)
Tabela19                <- Tablica_X[[1]]
Wiersze_do_boldowania19 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]

Tabela19[,2:17] <- lapply(Tabela19[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon20 <-kbl(Tabela19, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T, background = TloTotalTotal) %>% 
#column_spec(c(4),background = "#F6D5FF") %>% 
row_spec(Wiersze_do_boldowania19, bold = T) %>% # ,background = "#E3E3E3") %>% 
row_spec(podkreslanie, bold = T,hline_after=TRUE, background = "#C9C9C9") 

klon20 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon20)
klon20

```


\newpage

## CEEKAT/EKAT BY COUNTRY (YTD)


```{r EKAT_YTD, echo=FALSE}

Tablica_X             <- CreateTable(EKAT_YTD)
Tabela20                <- Tablica_X[[1]]
Wiersze_do_boldowania20 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]

Tabela20[,2:17] <- lapply(Tabela20[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon21 <-kbl(Tabela20, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4),background = "#F6D5FF") %>% 
row_spec(Wiersze_do_boldowania20, bold = T) %>% #,background = "#E3E3E3") %>% 
row_spec(podkreslanie, bold = T,hline_after=TRUE, background = "#C9C9C9") 

klon21 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon21)
klon21

```


\newpage

## CEEKAT/EKAT BY CUSTOMER (`r MiesiacAnalizyTekst`)


```{r EKAT_CUST, echo=FALSE}

Tablica_X               <- CreateTable(EKAT_CUSTOMERS)
Tabela21                <- Tablica_X[[1]]
Wiersze_do_boldowania21 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
Tabela21[,2:17]         <- lapply(Tabela21[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon22 <-kbl(Tabela21,longtable=T, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4),background = "#F6D5FF") %>% 
row_spec(Wiersze_do_boldowania21, bold = T) %>% #,background = "#E3E3E3") %>% 
row_spec(podkreslanie, bold = T,hline_after=TRUE) #, background = "#C9C9C9") 
klon22 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon22)
klon22

```

\newpage

## CEEKAT/EKAT BY CUSTOMER (YTD)


```{r EKAT_CUST_YTD, echo=FALSE}


Tablica_X             <- CreateTable(EKAT_CUSTOMERS_YTD)
Tabela22                <- Tablica_X[[1]]
Wiersze_do_boldowania22 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
Tabela22[,2:17] <- lapply(Tabela22[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon23 <-kbl(Tabela22,longtable=T, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4),background = "#F6D5FF") %>% 
row_spec(Wiersze_do_boldowania22, bold = T) %>% #,background = "#E3E3E3") %>% 
row_spec(podkreslanie, bold = T,hline_after=TRUE)#, background = "#C9C9C9") 
klon23 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon23)
klon23

```


\newpage

## TOP 20 MATERIAL GROUPS BY GROSS PROFIT (`r MiesiacAnalizyTekst`)

```{r TOP20GP, echo=FALSE}

Tablica_X               <- CreateTable(TOP20GP, nazwa_tabeli ="TOP20GP")
Tabela12                <- Tablica_X[[1]]
Wiersze_do_boldowania12 <- Tablica_X[[2]]

Tabela12[,2:17] <- lapply(Tabela12[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon10 <-kbl(Tabela12, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
column_spec(c(8),background = "#FFEBF9") %>% 
row_spec(Wiersze_do_boldowania12 , bold = T) %>%  #,background = "#E3E3E3") %>% 
row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal)

klon10 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon10)
klon10

```


```{r WykresTop20, fig.height=3.1,fig.width=10.5}
WykresPoloczony     <- TopBottom(TOP20GP,"TOP20")

WykresPoloczony
```


\newpage

## TOP 20 MATERIAL GROUPS BY GROSS PROFIT (YTD)

```{r TOP20GPYTD, echo=FALSE}

Tablica_X             <- CreateTable(TOP20GPYTD,nazwa_tabeli ="TOP20GPYTD")
Tabela13                <- Tablica_X[[1]]
Wiersze_do_boldowania13 <- Tablica_X[[2]]

Tabela13[,2:17] <- lapply(Tabela13[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon11 <-kbl(Tabela13, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
column_spec(c(8),background = "#FFEBF9") %>% 
 row_spec(Wiersze_do_boldowania13 , bold = T) %>% #,background = "#E3E3E3") %>%  
row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal)
klon11 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon11)
klon11

```

```{r WykresTop20y, fig.height=3.1,fig.width=10.5}
WykresPoloczony     <- TopBottom(TOP20GPYTD,"TOP20")

WykresPoloczony
```


\newpage

## TOP 20 MATERIAL GROUPS BY QUANTITY (`r MiesiacAnalizyTekst`)


```{r TOP20QUANT, echo=FALSE}

Tablica_X             <- CreateTable(TOP20QUANT,nazwa_tabeli ="TOP20QUANT")
Tabela14                <- Tablica_X[[1]]
Wiersze_do_boldowania14 <- Tablica_X[[2]]

Tabela14[,2:17] <- lapply(Tabela14[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon12 <-kbl(Tabela14, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
column_spec(c(4),background = "#FFEBF9")  %>% 
row_spec(Wiersze_do_boldowania14 , bold = T) %>% #,background = "#E3E3E3") %>% 
  row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal)

klon12 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon12)
klon12

```


```{r WykresTop20Q, fig.height=3.1,fig.width=10.5}
WykresPoloczony     <- TopBottom(TOP20QUANT,"TOP20")

WykresPoloczony
```




\newpage

## TOP 20 MATERIAL GROUPS BY QUANTITY (YTD)


```{r TOP20QUANT_YTD, echo=FALSE}

Tablica_X             <- CreateTable(TOP20QUANT_YTD,nazwa_tabeli ="TOP20QUANT_YTD")
Tabela15                <- Tablica_X[[1]]
Wiersze_do_boldowania15 <- Tablica_X[[2]]

Tabela15[,2:17] <- lapply(Tabela15[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon13 <-kbl(Tabela15, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
column_spec(c(4),background = "#FFEBF9")  %>% 
row_spec(Wiersze_do_boldowania15 , bold = T) %>% #,background = "#E3E3E3") %>% 
  row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal)

klon13 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon13)
klon13

```

```{r WykresTop20QY, fig.height=3.1,fig.width=10.5}
WykresPoloczony     <- TopBottom(TOP20QUANT_YTD,"TOP20")

WykresPoloczony
```





\newpage

## BOTTOM 20 MATERIAL GROUPS BY GROSS PROFIT (`r MiesiacAnalizyTekst`)


```{r BOTTOM20GP, echo=FALSE}

Tablica_X             <- CreateTable(BOTTOM20GP,nazwa_tabeli ="BOTTOM20GP")
Tabela16                <- Tablica_X[[1]]
Wiersze_do_boldowania16 <- Tablica_X[[2]]

Tabela16[,2:17] <- lapply(Tabela16[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon14 <-kbl(Tabela16, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
column_spec(c(8),background = "#FFEBF9") %>% 
row_spec(Wiersze_do_boldowania16 , bold = T) %>% #,background = "#E3E3E3")  %>% 
  row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal)

klon14 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon14)
klon14

```


```{r WykresBot, fig.height=3.1,fig.width=10.5}
WykresPoloczony     <- TopBottom(BOTTOM20GP,"BOTTOM20")

WykresPoloczony
```



\newpage

## BOTTOM 20 MATERIAL GROUPS BY GROSS PROFIT (YTD)


```{r BOTTOM20GP_YTD, echo=FALSE}

Tablica_X             <- CreateTable(BOTTOM20GP_YTD,nazwa_tabeli ="BOTTOM20GP_YTD")
Tabela16                <- Tablica_X[[1]]
Wiersze_do_boldowania16 <- Tablica_X[[2]]

Tabela16[,2:17] <- lapply(Tabela16[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon15 <-kbl(Tabela16, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
column_spec(c(8),background = "#FFEBF9")  %>% 
row_spec(Wiersze_do_boldowania16 , bold = T) %>% #,background = "#E3E3E3") %>% 
  row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal)

klon15 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon15)
klon15

```

```{r WykresBotY, fig.height=3.1,fig.width=10.5}
WykresPoloczony     <- TopBottom(BOTTOM20GP_YTD,"BOTTOM20")

WykresPoloczony
```




\newpage

## BOTTOM 20 MATERIAL GROUPS BY QUANTITY (`r MiesiacAnalizyTekst`)


```{r BOTTOM20QUANT, echo=FALSE}

Tablica_X             <- CreateTable(BOTTOM20QUANT,nazwa_tabeli = "BOTTOM20QUANT")
Tabela17                <- Tablica_X[[1]]
Wiersze_do_boldowania17 <- Tablica_X[[2]]

Tabela17[,2:17] <- lapply(Tabela17[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon16 <-kbl(Tabela17, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
column_spec(c(4),background = "#FFEBF9") %>% 
row_spec(Wiersze_do_boldowania17, bold = T) %>% #,background = "#E3E3E3")  %>% 
  row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal)

klon16 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon16)
klon16

```

```{r WykresBotQ, fig.height=3.1,fig.width=10.5}
WykresPoloczony     <- TopBottom(BOTTOM20QUANT,"BOTTOM20")

WykresPoloczony
```




\newpage

## BOTTOM 20 MATERIAL GROUPS BY QUANTITY (YTD)


```{r BOTTOM20QUANT_YTD, echo=FALSE}

Tablica_X             <- CreateTable(BOTTOM20QUANT_YTD,nazwa_tabeli = "BOTTOM20QUANT_YTD")
Tabela18                <- Tablica_X[[1]]
Wiersze_do_boldowania18 <- Tablica_X[[2]]

Tabela18[,2:17] <- lapply(Tabela18[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon17 <-kbl(Tabela18, booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
column_spec(c(4),background = "#FFEBF9")  %>% 
row_spec(Wiersze_do_boldowania18, bold = T) %>% #,background = "#E3E3E3") %>% 
  row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal)

klon17 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon17)
klon17

```


```{r WykresBotQY, fig.height=3.1,fig.width=10.5}
WykresPoloczony     <- TopBottom(BOTTOM20QUANT_YTD,"BOTTOM20")

WykresPoloczony
```




\newpage


## BBS BY COUNTRY (`r MiesiacAnalizyTekst`)

Total sales (3rd party + intercompany)
\vspace{-2mm}

```{r BBSMa, echo=FALSE}

Tablica_X               <- CreateTable(BBSM,nazwa_tabeli = "BBSM")
Tabela23                <- Tablica_X[[1]]
Wiersze_do_boldowania23 <- Tablica_X[[2]]

Tabela23[,2:17] <- lapply(Tabela23[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon18<-kbl(Tabela23, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%  
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania23, bold = T,background = "#E3E3E3") %>% 
  row_spec(nrow(Tablica_X[[1]]), bold = T)#,background = TloTotalTotal)

klon18 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon18)
klon18

```


## BBS BY COUNTRY (YTD)


```{r BBSM_YTD, echo=FALSE}

Tablica_X               <- CreateTable(BBSM_YTD,nazwa_tabeli = "BBSM_YTD")
Tabela26                <- Tablica_X[[1]]
Wiersze_do_boldowania26 <- Tablica_X[[2]]

Tabela26[,2:17] <- lapply(Tabela26[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon30         <- kbl(Tabela26, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania26, bold = T,background = "#E3E3E3")# %>% 
#row_spec(nrow(Tablica_X[[1]]), bold = T)#,background = TloTotalTotal)

klon30 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon30)
klon30

```



\newpage


## BBS BY EUROPEAN INDUSTRY (`r MiesiacAnalizyTekst`)


```{r BBS_EI, echo=FALSE}

Tablica_X             <- CreateTable(BBS_EI,nazwa_tabeli = "BBS_EI")
Tabela24                <- Tablica_X[[1]]
Wiersze_do_boldowania24 <- Tablica_X[[2]]

Tabela24[,2:17] <- lapply(Tabela24[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon19<-kbl(Tabela24, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),align=FormatKolumnyOddzielone,linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania24, bold = T,background = "#E3E3E3") %>% row_spec(nrow(Tablica_X[[1]]), bold = T)#,background = TloTotalTotal) 

klon19 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon19)
klon19


```



<!-- \newpage -->
<!-- ## BBS RESULTS BY KEY CUSTOMERS (`r MiesiacAnalizyTekst`) -->

<!-- ```{r BBS_KEY, echo=FALSE} -->

<!-- Tablica_X             <- CreateTable(BBS_KEY) -->
<!-- Tabela25                <- Tablica_X[[1]] -->
<!-- Wiersze_do_boldowania25 <- Tablica_X[[2]] -->

<!-- Tabela25[,2:17] <- lapply(Tabela25[,2:17], function(x) { -->
<!-- cell_spec(x, -->
<!-- color = ifelse(x<0,"#C815E0","black")) -->
<!-- }) -->

<!-- klon20 <-kbl(Tabela25,booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),align=FormatKolumnyOddzielone,linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>%  -->
<!-- #column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>%  -->

<!-- row_spec(Wiersze_do_boldowania25, bold = T,background = "#E3E3E3") -->

<!-- klon20 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon20) -->
<!-- klon20 -->



<!-- ``` -->


## BBS BY EUROPEAN INDUSTRY (YTD)


```{r BBS_EI_YTD, echo=FALSE}

Tablica_X             <- CreateTable(BBS_EI_YTD,nazwa_tabeli = "BBS_EI_YTD")
Tabela27                <- Tablica_X[[1]]
Wiersze_do_boldowania27 <- Tablica_X[[2]]

Tabela27[,2:17] <- lapply(Tabela27[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon31<-kbl(Tabela27, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),align=FormatKolumnyOddzielone,linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania27, bold = T,background = "#E3E3E3") %>% 
row_spec(nrow(Tablica_X[[1]]), bold = T)#,background = TloTotalTotal)


klon31 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon31)
klon31


```


\newpage
## BBS BY KEY CUSTOMERS (YTD)

```{r BBS_KEY_YTD, echo=FALSE}

Tablica_X             <- CreateTable(BBS_KEY_YTD,nazwa_tabeli = "BBS_KEY_YTD")
Tabela28                <- Tablica_X[[1]]
Wiersze_do_boldowania28 <- Tablica_X[[2]]

Tabela28[,2:17] <- lapply(Tabela28[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon32 <-kbl(Tabela28,booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),align=FormatKolumnyOddzielone,linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%  
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 

row_spec(Wiersze_do_boldowania28, bold = T,hline_after=TRUE) %>% #,background = "#E3E3E3") %>% 
row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) 

klon32 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon32)
klon32



```

\newpage


## WATER TREATMENT: WATER TREATMENT INDUSTRY + CROSS SELLING (`r MiesiacAnalizyTekst`)



```{r WT_TOTAL, echo=FALSE}

Tablica_X             <- CreateTable(WT_TOTAL)
Tabela29                <- Tablica_X[[1]]
Wiersze_do_boldowania29 <- Tablica_X[[2]]

Tabela29[,2:17] <- lapply(Tabela29[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon33<-kbl(Tabela29, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania29, bold = T,background = "#E3E3E3") %>% 
  row_spec(nrow(Tablica_X[[1]]), bold = T)#,background = TloTotalTotal) 

klon33 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon33)
klon33

```

## WATER TREATMENT: WATER TREATMENT INDUSTRY + CROSS SELLING (YTD)


```{r WT_TOTAL_YTD, echo=FALSE}

Tablica_X             <- CreateTable(WT_TOTAL_YTD)
Tabela30                <- Tablica_X[[1]]
Wiersze_do_boldowania30 <- Tablica_X[[2]]


Tabela30[,2:17] <- lapply(Tabela30[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon34<-kbl(Tabela30, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania30, bold = T,background = "#E3E3E3") %>% 
    row_spec(nrow(Tablica_X[[1]]), bold = T)#,background = TloTotalTotal) 

klon34 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon34)
klon34

```




\newpage
## WATER TREATMENT: CROSS SELLING BY COUNTRY (`r MiesiacAnalizyTekst`)

```{r WT_CROSS, echo=FALSE}

Tablica_X             <- CreateTable(WT_CROSS)
Tabela31                <- Tablica_X[[1]]
Wiersze_do_boldowania31 <- Tablica_X[[2]]

Tabela31[,2:17] <- lapply(Tabela31[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon35<-kbl(Tabela31, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%  
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania31, bold = T,background = "#E3E3E3") %>% 
 row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) 


klon35 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon35)
klon35

```

\vspace{5mm}
## WATER TREATMENT: CROSS SELLING BY COUNTRY (YTD)

```{r WT_CROSS_YTD, echo=FALSE}

Tablica_X             <- CreateTable(WT_CROSS_YTD)
Tabela32                <- Tablica_X[[1]]
Wiersze_do_boldowania32 <- Tablica_X[[2]]

Tabela32[,2:17] <- lapply(Tabela32[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon36<-kbl(Tabela32, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania32, bold = T,background = "#E3E3E3") %>% 
  row_spec(nrow(Tablica_X[[1]]), bold = T)#,background = TloTotalTotal) 

klon36 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon36)
klon36

```



\newpage
<!-- \vspace{5mm} -->

## WATER TREATMENT: CROSS SELLING BY SALES PART/CHANNEL (`r MiesiacAnalizyTekst`)

```{r WT_THIRD, echo=FALSE}

Tablica_X             <- CreateTable(WT_THIRD,nazwa_tabeli = "WT_THIRD")
Tabela33                <- Tablica_X[[1]]
Wiersze_do_boldowania33 <- Tablica_X[[2]]

Tabela33[,2:17] <- lapply(Tabela33[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon36<-kbl(Tabela33, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania33,hline_after = TRUE, bold = T)#,background = "#E3E3E3")

klon36 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon36)
klon36

```

\newpage

## WATER TREATMENT: CROSS SELLING BY SALES PART/CHANNEL (YTD)

\vspace{5mm}

```{r WT_THIRD_YTD, echo=FALSE}

Tablica_X             <- CreateTable(WT_THIRD_YTD, nazwa_tabeli = "WT_THIRD_YTD")
Tabela34                <- Tablica_X[[1]]
Wiersze_do_boldowania34 <- Tablica_X[[2]]

Tabela34[,2:17] <- lapply(Tabela34[,2:17], function(x) {
cell_spec(x, color = ifelse(x<0,"#C815E0","black"))
})

klon37<-kbl(Tabela34, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania34, bold = T, hline_after=TRUE)#,background = "#E3E3E3")

klon37 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon37)
klon37

```



\newpage

##  WATER TREATMENT: CROSS SELLING BY INDUSTRY (`r MiesiacAnalizyTekst`)


```{r WT_CS_IND, echo=FALSE}

Tablica_X             <- CreateTable(WT_CS_IND)
Tabela35                <- Tablica_X[[1]]
Wiersze_do_boldowania35 <- Tablica_X[[2]]

Tabela35[,2:17] <- lapply(Tabela35[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon38<-kbl(Tabela35, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%  
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania35, bold = T,background = "#E3E3E3") %>% 
   row_spec(nrow(Tablica_X[[1]]), bold = T)#,background = TloTotalTotal) 

klon38 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon38)
klon38

```


\newpage

## WATER TREATMENT: CROSS SELLING BY INDUSTRY (YTD)


```{r WT_CS_IND_YTD, echo=FALSE}

Tablica_X             <- CreateTable(WT_CS_IND_YTD)
Tabela36                <- Tablica_X[[1]]
Wiersze_do_boldowania36 <- Tablica_X[[2]]

Tabela36[,2:17] <- lapply(Tabela36[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon39<-kbl(Tabela36, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania36, bold = T,background = "#E3E3E3") %>% 
  row_spec(nrow(Tablica_X[[1]]), bold = T)#,background = TloTotalTotal) 

klon39 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon39)
klon39

```


\newpage
## WATER TREATMENT INDUSTRY BY COUNTRY (`r MiesiacAnalizyTekst`)

```{r WT_INDUSTRY, echo=FALSE}

Tablica_X             <- CreateTable(WT_INDUSTRY)
Tabela37                <- Tablica_X[[1]]
Wiersze_do_boldowania37 <- Tablica_X[[2]]

Tabela37[,2:17] <- lapply(Tabela37[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon40<-kbl(Tabela37, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%  
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania37, bold = T,background = "#E3E3E3") %>% 
   row_spec(nrow(Tablica_X[[1]]), bold = T)#,background = TloTotalTotal) 

klon40 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon40)
klon40

```

## WATER TREATMENT INDUSTRY BY COUNTRY (YTD)

```{r WT_INDUSTRY_YTD, echo=FALSE}

Tablica_X             <- CreateTable(WT_INDUSTRY_YTD)
Tabela38                <- Tablica_X[[1]]
Wiersze_do_boldowania38 <- Tablica_X[[2]]

Tabela38[,2:17] <- lapply(Tabela38[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon41<-kbl(Tabela38, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%  
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania38, bold = T,background = "#E3E3E3") %>% 
   row_spec(nrow(Tablica_X[[1]]), bold = T)#,background = TloTotalTotal) 

klon41 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon41)
klon41

```


\newgeometry{top=1.5cm,bottom=1cm,right=4cm,left=1.5cm}
\newpage

\newgeometry{top=1.5cm,bottom=1cm,right=4cm,left=1.5cm}
\thispagestyle{empty}
# BES|BSP RESULTS

\vspace{-1.7cm}
\rule{730pt}{1.5pt}

\thispagestyle{empty}
\newgeometry{top=1.5cm,bottom=1.3cm,right=0.8cm,left=0.8cm}
\newpage

## BES|BSP PRODUCT DIVISION AND MATERIAL TYPE (`r MiesiacAnalizyTekst`)

Monthly - Total sales (3rd party + intercompany*)
```{r COUNTRIESBYINDUSTESy}

Tablica_X               <- CreateTable(BESBSP_PD_MT,nazwa_tabeli ="BESBSP_PD_MT")
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]

Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T, hline_after=TRUE)

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```
* ES-essentials, SP-specialties; based on local classification - dependent ONLY on product parameters&local decisions, not connected with customer/industryProduc Division - final division of SD transaction results allocation; dependent on material & customer industry; based on central product basket allocation file

## BES|BSP PRODUCT DIVISION AND MATERIAL TYPE (YTD)
```{r COUNTRIESBYINDUSTRI}

Tablica_X               <- CreateTable(BESBSP_PD_MT_YTD,nazwa_tabeli ="BESBSP_PD_MT_YTD")
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]

Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE)

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```

\newpage
## BES|BSP COUNTRIES BY DIVISION (`r MiesiacAnalizyTekst`)

Monthly - Total sales (3rd party + intercompany*)
```{r COUNTRIESBYINDTESy}

Tablica_X               <- CreateTable(BESBSP_CRD,nazwa_tabeli = "BESBSP_CRD")
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]

Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE)

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```

\newpage

## BES|BSP COUNTRIES BY DIVISION (YTD)

```{r COUNTRIEINDUSTRI}

Tablica_X               <- CreateTable(BESBSP_CRD_YTD,nazwa_tabeli = "BESBSP_CRD_YTD")
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]

Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T, hline_after=TRUE)

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```

\newpage
## BES|BSP SUBSIDIARIES BY PRODUCT DIVISION (`r MiesiacAnalizyTekst`)

Monthly - Total sales (3rd party + intercompany*)
```{r COUNTRSBYINDTESy}

Tablica_X               <- CreateTable(BESBSP_SR,nazwa_tabeli ="BESBSP_SR")
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE) %>% 
row_spec(podkreslanie, bold = T, background = "#C9C9C9")


klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```

\newpage

## BES|BSP SUBSIDIARIES BY PRODUCT DIVISION (YTD)

```{r COUNTRINDUSTRI}

Tablica_X               <- CreateTable(BESBSP_SR_YTD,nazwa_tabeli ="BESBSP_SR_YTD")
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE) %>% 
row_spec(podkreslanie, bold = T, background = "#C9C9C9")

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```


\newpage
## BES|BSP IC-CPM GROUPS BY PRODUCT DIVISION AND MATERIAL TYPE (`r MiesiacAnalizyTekst`)

```{r COUNTRIUSTRI}

Tablica_X               <- CreateTable(BESBSP_ICCPM,nazwa_tabeli ="BESBSP_ICCPM")
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
Tabela40[,2:17]         <- lapply(Tabela40[,2:17], function(x) {cell_spec(x,color = ifelse(x<0,"#C815E0","black"))})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>% row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE) %>% 
row_spec(podkreslanie, bold = T, background = "#C9C9C9")

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```




\newpage
## BES|BSP IC-CPM GROUPS BY PRODUCT DIVISION AND MATERIAL TYPE (YTD)

```{r COUNTRISTRI}

Tablica_X               <- CreateTable(BESBSP_ICCPM_YTD,nazwa_tabeli ="BESBSP_ICCPM_YTD")
Tabela41                <- Tablica_X[[1]]
Wiersze_do_boldowania41 <- Tablica_X[[2]]
podkreslanie1            <- Tablica_X[[3]]
Tabela41[,2:17] <- lapply(Tabela41[,2:17], function(x) {cell_spec(x,color = ifelse(x<0,"#C815E0","black"))})

klon44 <- kbl(Tabela41, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania41, bold = T,hline_after=TRUE) %>% 
row_spec(podkreslanie1, bold = T,background = "#C9C9C9")#, background = "#C9C9C9")

klon44 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon44)
klon44

```




\newpage
## BES|BSP PRODUCT DIVISIONS BY IC-CPM AND MATERIAL TYPE (`r MiesiacAnalizyTekst`)

```{r COTRIUSTRI}

Tablica_X               <- CreateTable(BESBSP_PDICCPM,nazwa_tabeli = "BESBSP_PDICCPM")
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE) %>% 
row_spec(podkreslanie, bold = T, background = "#C9C9C9")

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```




\newpage
## BES|BSP PRODUCT DIVISIONS BY IC-CPM AND MATERIAL TYPE (YTD)

```{r COUNTRIRI}

Tablica_X               <- CreateTable(BESBSP_PDICCPM_YTD,nazwa_tabeli = "BESBSP_PDICCPM")
Tabela40                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
Tabela40[,2:17] <- lapply(Tabela40[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

klon43 <- kbl(Tabela40, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
#column_spec(c(4,5,8,9,12,13,16,17),background = "#E7EAFF") %>% 
row_spec(Wiersze_do_boldowania40, bold = T,hline_after=TRUE) %>% 
row_spec(podkreslanie, bold = T, background = "#C9C9C9") 

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```




\newpage
## BES|BSP INDUSTRIES BY PRODUCT DIVISION (`r MiesiacAnalizyTekst`)

Monthly - Total sales (3rd party + intercompany*)
```{r COUNTRSBYDTESy}

Tablica_X               <- CreateTable(BESBSP_IRPD,nazwa_tabeli = "BESBSP_IRPD")
Tabela41                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
BoldowaniePomocnicze    <- Tablica_X[[4]]


Tabela41[,2:17]         <- lapply(Tabela41[,2:17], function(x) {
                                  cell_spec(x,
                                  color = ifelse(x<0,"#C815E0","black"))
                                  })

do_kolorow<-data.frame(nazwa_kategorii="",odWiersza=as.numeric("0"),doWiersza=as.numeric("0"))
for(dlugosc in 1: length(BoldowaniePomocnicze)){
  z                    <- str_count(BoldowaniePomocnicze[dlugosc],"[0-9]")
  dlugoscNazwyKategori <- nchar(BoldowaniePomocnicze[dlugosc])-z
 
  do_kolorow[nrow(do_kolorow)+1,] <- list(str_sub(BoldowaniePomocnicze[dlugosc],1,dlugoscNazwyKategori),
                                      do_kolorow[nrow(do_kolorow),3] + 1,
                                      do_kolorow[nrow(do_kolorow),3] +          as.numeric(str_sub(BoldowaniePomocnicze[dlugosc],(nchar(BoldowaniePomocnicze[dlugosc])-z)+1,nchar(BoldowaniePomocnicze[dlugosc]))) )
  
}
 
do_kolorow <- do_kolorow[2:nrow(do_kolorow),]


klon43 <- kbl(Tabela41, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T)  %>% 


row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
  
  
row_spec(Wiersze_do_boldowania40 ,bold = T) %>% # ,background = "#E3E3E3") %>%

# row_spec(do_kolorow[1,2]:do_kolorow[1,3],background = pAleta[1]) %>%
# row_spec(do_kolorow[2,2]:do_kolorow[2,3],background = pAleta[2]) %>%
# row_spec(do_kolorow[3,2]:do_kolorow[3,3],background = pAleta[3]) %>%
# row_spec(do_kolorow[4,2]:do_kolorow[4,3],background = pAleta[4]) %>%
# row_spec(do_kolorow[5,2]:do_kolorow[5,3],background = pAleta[5]) %>%
# row_spec(do_kolorow[6,2]:do_kolorow[6,3],background = pAleta[6]) %>%
# row_spec(do_kolorow[7,2]:do_kolorow[7,3],background = pAleta[7]) %>%

pack_rows(do_kolorow[1,1],do_kolorow[1,2],do_kolorow[1,3], latex_gap_space = "0.7em", background = pAleta2[5]) %>%
pack_rows(do_kolorow[2,1],do_kolorow[2,2],do_kolorow[2,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>% 
pack_rows(do_kolorow[3,1],do_kolorow[3,2],do_kolorow[3,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>%
pack_rows(do_kolorow[4,1],do_kolorow[4,2],do_kolorow[4,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>%
pack_rows(do_kolorow[5,1],do_kolorow[5,2],do_kolorow[5,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>% 
pack_rows(do_kolorow[6,1],do_kolorow[6,2],do_kolorow[6,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>% 
pack_rows(do_kolorow[7,1],do_kolorow[7,2],do_kolorow[7,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>% 

row_spec(podkreslanie, bold = T, background = "#C9C9C9")


klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43

```

\newpage

## BES|BSP INDUSTRIES BY PRODUCT DIVISION (YTD)

```{r COUNTRINDTRI}

Tablica_X               <- CreateTable(BESBSP_IRPD_YTD,nazwa_tabeli = "BESBSP_IRPD_YTD")
Tabela41                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
BoldowaniePomocnicze    <- Tablica_X[[4]]


Tabela41[,2:17]         <- lapply(Tabela41[,2:17], function(x) {
                                  cell_spec(x,
                                  color = ifelse(x<0,"#C815E0","black"))
                                  })

do_kolorow<-data.frame(nazwa_kategorii="",odWiersza=as.numeric("0"),doWiersza=as.numeric("0"))
for(dlugosc in 1: length(BoldowaniePomocnicze)){
  z                    <- str_count(BoldowaniePomocnicze[dlugosc],"[0-9]")
  dlugoscNazwyKategori <- nchar(BoldowaniePomocnicze[dlugosc])-z
 
  do_kolorow[nrow(do_kolorow)+1,] <- list(str_sub(BoldowaniePomocnicze[dlugosc],1,dlugoscNazwyKategori),
                                      do_kolorow[nrow(do_kolorow),3] + 1,
                                      do_kolorow[nrow(do_kolorow),3] +          as.numeric(str_sub(BoldowaniePomocnicze[dlugosc],(nchar(BoldowaniePomocnicze[dlugosc])-z)+1,nchar(BoldowaniePomocnicze[dlugosc]))) )
  
}
 
do_kolorow <- do_kolorow[2:nrow(do_kolorow),]


klon43 <- kbl(Tabela41, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header"))   %>% 


row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
  
  
row_spec(Wiersze_do_boldowania40, bold = T) %>% # ,background = "#E3E3E3") %>%

  # 
# row_spec(do_kolorow[1,2]:do_kolorow[1,3],background = pAleta[1]) %>%
# row_spec(do_kolorow[2,2]:do_kolorow[2,3],background = pAleta[2]) %>%
# row_spec(do_kolorow[3,2]:do_kolorow[3,3],background = pAleta[3]) %>%
# row_spec(do_kolorow[4,2]:do_kolorow[4,3],background = pAleta[4]) %>%
# row_spec(do_kolorow[5,2]:do_kolorow[5,3],background = pAleta[5]) %>%
# row_spec(do_kolorow[6,2]:do_kolorow[6,3],background = pAleta[6]) %>%
# row_spec(do_kolorow[7,2]:do_kolorow[7,3],background = pAleta[7]) %>%
#   
# row_spec(do_kolorow[1,2]:do_kolorow[1,3]) %>%
# row_spec(do_kolorow[2,2]:do_kolorow[2,3]) %>%
# row_spec(do_kolorow[3,2]:do_kolorow[3,3]) %>%
# row_spec(do_kolorow[4,2]:do_kolorow[4,3]) %>%
# row_spec(do_kolorow[5,2]:do_kolorow[5,3]) %>%
# row_spec(do_kolorow[6,2]:do_kolorow[6,3]) %>%
# row_spec(do_kolorow[7,2]:do_kolorow[7,3]) %>%

pack_rows(do_kolorow[1,1],do_kolorow[1,2],do_kolorow[1,3], latex_gap_space = "0.7em", background = pAleta2[5]) %>%
pack_rows(do_kolorow[2,1],do_kolorow[2,2],do_kolorow[2,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>% 
pack_rows(do_kolorow[3,1],do_kolorow[3,2],do_kolorow[3,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>%
pack_rows(do_kolorow[4,1],do_kolorow[4,2],do_kolorow[4,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>%
pack_rows(do_kolorow[5,1],do_kolorow[5,2],do_kolorow[5,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>% 
pack_rows(do_kolorow[6,1],do_kolorow[6,2],do_kolorow[6,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>% 
pack_rows(do_kolorow[7,1],do_kolorow[7,2],do_kolorow[7,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>% 

row_spec(podkreslanie, bold = T, background = "#C9C9C9") %>% 
  
add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T)

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43
```



\newpage
## BES|BSP DIVISIONS BY INDUSTRY (`r MiesiacAnalizyTekst`)

Monthly - Total sales (3rd party + intercompany*)
```{r COUTRSBYTESy}


Tablica_X               <- CreateTable(BESBSP_DI,nazwa_tabeli = "BESBSP_DI")
Tabela41                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
BoldowaniePomocnicze    <- Tablica_X[[4]]


Tabela41[,2:17]         <- lapply(Tabela41[,2:17], function(x) {
                                  cell_spec(x,
                                  color = ifelse(x<0,"#C815E0","black"))
                                  })

do_kolorow <-data.frame(nazwa_kategorii="",odWiersza=as.numeric("0"),doWiersza=as.numeric("0"))
for(dlugosc in 1: length(BoldowaniePomocnicze)){
  z                               <- str_count(BoldowaniePomocnicze[dlugosc],"[0-9]")
  dlugoscNazwyKategori            <- nchar(BoldowaniePomocnicze[dlugosc])-z
  do_kolorow[nrow(do_kolorow)+1,] <- list(str_sub(BoldowaniePomocnicze[dlugosc],1,dlugoscNazwyKategori),
                                      do_kolorow[nrow(do_kolorow),3] + 1,
                                      do_kolorow[nrow(do_kolorow),3] +          as.numeric(str_sub(BoldowaniePomocnicze[dlugosc],(nchar(BoldowaniePomocnicze[dlugosc])-z)+1,nchar(BoldowaniePomocnicze[dlugosc]))) )
  
}
 
do_kolorow <- do_kolorow[2:nrow(do_kolorow),]


klon43 <- kbl(Tabela41, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T)  %>% 


row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
  
  
row_spec(Wiersze_do_boldowania40, bold = T) %>% # ,background = "#E3E3E3") %>%

# row_spec(do_kolorow[1,2]:do_kolorow[1,3],background = pAleta[1]) %>%
# row_spec(do_kolorow[2,2]:do_kolorow[2,3],background = pAleta[2]) %>%
# row_spec(do_kolorow[3,2]:do_kolorow[3,3],background = pAleta[3]) %>%


pack_rows(do_kolorow[1,1],do_kolorow[1,2],do_kolorow[1,3], latex_gap_space = "0.7em", background = pAleta2[5]) %>%
pack_rows(do_kolorow[2,1],do_kolorow[2,2],do_kolorow[2,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>% 
pack_rows(do_kolorow[3,1],do_kolorow[3,2],do_kolorow[3,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>%   

row_spec(podkreslanie, bold = T, background = "#C9C9C9")

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43
```

\newpage

## BES|BSP DIVISIONS BY INDUSTRY (YTD)

```{r COUNTRITRI}

Tablica_X               <- CreateTable(BESBSP_DI_YTD,nazwa_tabeli = "BESBSP_DI_YTD")
Tabela41                <- Tablica_X[[1]]
Wiersze_do_boldowania40 <- Tablica_X[[2]]
podkreslanie            <- Tablica_X[[3]]
BoldowaniePomocnicze    <- Tablica_X[[4]]


Tabela41[,2:17]         <- lapply(Tabela41[,2:17], function(x) {
                                  cell_spec(x,
                                  color = ifelse(x<0,"#C815E0","black"))
                                  })

do_kolorow<-data.frame(nazwa_kategorii="",odWiersza=as.numeric("0"),doWiersza=as.numeric("0"))
for(dlugosc in 1: length(BoldowaniePomocnicze)){
  z                    <- str_count(BoldowaniePomocnicze[dlugosc],"[0-9]")
  dlugoscNazwyKategori <- nchar(BoldowaniePomocnicze[dlugosc])-z
 
  do_kolorow[nrow(do_kolorow)+1,] <- list(str_sub(BoldowaniePomocnicze[dlugosc],1,dlugoscNazwyKategori),
                                      do_kolorow[nrow(do_kolorow),3] + 1,
                                      do_kolorow[nrow(do_kolorow),3] +          as.numeric(str_sub(BoldowaniePomocnicze[dlugosc],(nchar(BoldowaniePomocnicze[dlugosc])-z)+1,nchar(BoldowaniePomocnicze[dlugosc]))) )
  
}
 
do_kolorow <- do_kolorow[2:nrow(do_kolorow),]


klon43 <- kbl(Tabela41, longtable=TRUE, booktabs = T,escape = FALSE, col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "",align=FormatKolumnyOddzielone) %>% kable_styling(latex_options = c("hold_position", "repeat_header")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T)  %>% 


row_spec(nrow(Tablica_X[[1]]), bold = T,background = TloTotalTotal) %>% 
  
  
row_spec(Wiersze_do_boldowania40, bold = T) %>% # ,background = "#E3E3E3") %>%

# row_spec(do_kolorow[1,2]:do_kolorow[1,3],background = pAleta[1]) %>%
# row_spec(do_kolorow[2,2]:do_kolorow[2,3],background = pAleta[2]) %>%
# row_spec(do_kolorow[3,2]:do_kolorow[3,3],background = pAleta[3]) %>%



pack_rows(do_kolorow[1,1],do_kolorow[1,2],do_kolorow[1,3], latex_gap_space = "0.7em", background = pAleta2[5]) %>%
pack_rows(do_kolorow[2,1],do_kolorow[2,2],do_kolorow[2,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>% 
pack_rows(do_kolorow[3,1],do_kolorow[3,2],do_kolorow[3,3], latex_gap_space = "1.2em", background = pAleta2[5]) %>% 
row_spec(podkreslanie, bold = T, background = "#C9C9C9") 

klon43 <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",klon43)
klon43
```






\newgeometry{top=1.5cm,bottom=1cm,right=4cm,left=1.5cm}

\newpage
\thispagestyle{empty}
# COMMENTS
\vspace{-1.7cm}
\rule{730pt}{1.5pt}


\newpage

SOON


<!-- \rule{730pt}{1.5pt} -->
<!-- \thispagestyle{empty} -->

<!-- \newgeometry{top=1.5cm,bottom=1.3cm,right=4cm,left=0.8cm} -->
<!-- \newpage -->
<!-- ## KEY FACTORS THAT IMPACT THE RESULT -->
<!-- ### BALTICS -->

<!-- \newpage -->
<!-- ### BULGARIA -->

<!-- \newpage -->
<!-- ### CROATIA|SLOVENIA -->

<!-- \newpage -->
<!-- ### HUNGARY -->


\thispagestyle{empty}


crosschecking raport:



OK!


time of raport creation: \pdfdate


pilot
patchwork
packages

