---
date: "March 22, 2005"
title: "Performance report"
author: Andrzej Kopec (andrzej.kopec@brenntag.pl)
geometry: left=1cm,right=1cm,top=0.5cm,bottom=1cm, a4paper
documentclass: report
classoption: landscape
header-includes:
- \AtBeginDocument{\let\maketitle\relax}
 # % Allows me to use and print accented characters (document is in Spanish)
- \usepackage[T1]{fontenc}
- \usepackage[utf8]{inputenc}
 # % It allows me to place the tables or images where I want, whether there is space or not
- \usepackage{float}
 # % It has several commands to have more control over the tables (at least I use it for this)
- \usepackage{array}
 # % For custom headers and footers
- \usepackage{fancyhdr}
#  % This line allows me to manipulate images within latex
- \usepackage{graphicx}
 # % This package has several uses, for this document I used it to manage hyperlinks and introduce metadata to the document
 # % These lines define the font that I want to use in the document
- \usepackage{caption} #  æeby schować numery tabel a zostawić tylko opis
- \usepackage{helvet}
- \renewcommand{\familydefault}{\sfdefault}
- \usepackage{datetime}
- \usepackage{numprint}
- \usepackage{parskip}
- \usepackage{siunitx}
- \usepackage{pdflscape}
- \usepackage{svg}
- \usepackage{xstring}
- \usepackage{fontspec}
- \usepackage{fontsize}
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{titlesec}
- \usepackage[titletoc]{appendix}
- \usepackage{wrapfig}
- \usepackage{tgheros}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage[singlelinecheck=false]{caption}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{lipsum}  
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{afterpage}
#- \usepackage{helvet}
#- \renewcommand\familydefault{\sfdefault}
#- \usepackage[polish]{babel}
#- \setmainfont{72}
- \usepackage{setspace}
- \usepackage{amsmath, booktabs, caption, longtable}
#- \setlength{\headheight}{13pt}
- \pagestyle{fancy}
- \lfoot{\fontsize{6pt}{11pt}\selectfont STRICLY CONFIDENTIAL. SHARING WITH UNAUTHORIZED PERSONS IS NOT PERMITTED}
- \rfoot{\fontsize{6pt}{11pt}\selectfont {\thepage}}
- \rhead{\includegraphics[width=35mm]{BrenntagPurple.png}\vspace{-8mm}}
- \renewcommand{\headrulewidth}{0pt}
- \cfoot{}
- \chead{}
- \lhead{}
# - \rhead{}   żeby nic się nie pojawiało po prawej stronie nagłówka strony
# - \setcounter{secnumdepth}{0} #gubią się odniesienia 
- \usepackage[export]{adjustbox}
- \setlength\parindent{24pt}
- \renewcommand{\contentsname}{Table of contents} 
- \usepackage{hyperref} #ten pakiet musi być ładowany  na końcu
# - \makeatletter
# - \renewcommand{\@seccntformat}[0]{}
# - \makeatother



output:
  pdf_document:
    keep_tex: yes
    latex_engine: xelatex
    number_sections: yes

---


\titleformat{\chapter}[display]
  {\normalfont\bfseries}{}{0pt}{\Huge}
  
\thispagestyle{empty}
\definecolor{Brenntag}{RGB}{26, 0, 51}
\pagecolor{Brenntag}\afterpage{\nopagecolor}
\fontfamily{qhv}
\fontsize{12}{23}
<!-- \fontsize{12}{22} -->

\selectfont
\captionsetup[table]{labelformat=empty}

<!-- \vspace{10mm} -->


<!-- \addtocontents{toc}{\protect\newpage} -->
<!-- <!-- \noindent\makebox[\linewidth]{\rule{\paperwidth}{0.8pt}} --> -->

<!-- <!-- \noindent\rule{25cm}{0.4pt} --> -->



\textbf{\textcolor{white}{\HUGE BRENNTAG CEE PERFORMANCE REPORT}}
\vspace{-4mm}

\textbf{\textcolor{white}{\small `r paste(MiesiacAnalizyTekst,RokAnalizy,sep=" ")`}}

\vspace{10mm}
\includegraphics[width=330pt]{BREN.png} 

<!-- \makebox[\textheight]{\includegraphics[width=\textheight]{BREN2.png}} -->


\newpage

\newgeometry{top=1.5cm,bottom=0.8cm,right=4cm,left=1.5cm}


\thispagestyle{empty}



\footnotesize \tableofcontents

\thispagestyle{empty}

\newpage
\newgeometry{top=1.5cm,bottom=1cm,right=4cm,left=1.5cm}



\thispagestyle{empty}
# CEE TOTAL RESULT
\vspace{-1.7cm}
\rule{730pt}{1.5pt}


\thispagestyle{empty}


\newpage
\newgeometry{top=1.5cm,bottom=1.3cm,right=0.8cm,left=0.8cm}
```{r seewtup, include=FALSE,cache=FALSE}
knitr::opts_chunk$set(cache = FALSE,echo = FALSE,warning = FALSE,error = FALSE,comment = FALSE)
```

\npthousandsep{\,}

## TOTAL RESULT (`r MiesiacAnalizyTekst`)

<!-- \vspace{-4mm} -->

<!-- \leftskip 36pt  \scriptsize 3rd party + intercompany -->
<!-- \vspace{-1mm} -->
<!-- \leftskip 0pt -->

```{r MAINTOsdsTAL, echo=FALSE,warning=FALSE}
Tablica_X             <-  CreateTable(BESBSP_IRPD_YTD,nazwa_tabeli = "BESBSP_IRPD_YTD")
Tabela                <- Tablica_X[[1]]
Wiersze_do_boldowania <- Tablica_X[[2]]

Quant         <- Tabela[nrow(Tabela),2]
Quant_PRV     <- Tabela[nrow(Tabela),3]
GrossProf     <- Tabela[nrow(Tabela),6]
GrossProf_PRV <- Tabela[nrow(Tabela),7]
Turnov        <- Tabela[nrow(Tabela),10]
Turnov_PRV    <- Tabela[nrow(Tabela),11]
GPMT          <- Tabela[nrow(Tabela),14]
GPMT_PRV      <- Tabela[nrow(Tabela),15]
options(knitr.table.format = "latex")

Tabela        <- as.data.frame(Tabela)
roW=5
columN=4


Tabela[,2:17] <- lapply(Tabela[,2:17], function(x) {
cell_spec(x,
color = ifelse(x<0,"#C815E0","black"))
})

Kraj1<-"BELGIA"
Kraj1<-paste("\\#",Kraj1,sep="")

Tabela[Tabela$SubRegion=="Poland",4] <-paste("\\underline{", Tabela[Tabela$SubRegion=="Poland",4], "}",sep="")
Tabela[Tabela$SubRegion=="Poland",4] <-paste0("\\href{", "produkty.html",Kraj1, "}","{", Tabela[Tabela$SubRegion=="Poland",4], "}")
#Tabela[roW,columN]<-paste0(paste("\\href{", "the_plik.html", "}","{",Kraj1,"}",sep=""),"{", Tabela[roW,columN], "}")


zen <-kbl(Tabela,  booktabs = T,escape = FALSE, align=FormatKolumnyOddzielone,col.names=c(" ",rep(c("ActYear","PreYear","YearToY","YearToY"),4)),linesep = "") %>% kable_styling(latex_options = c("hold_position","scale_down")) %>% add_header_above(c(" "=1,"QUANTITY MT"=4, "GROSS PROFIT TEUR"=4,"TURNOVER TEUR"=4, "GP|MT"=4),bold = T) %>%   
row_spec(Wiersze_do_boldowania, bold = T)  %>% #, background = "#E3E3E3") %>%       WYBOLDOWANIE POWINNO BYĆ SPARAMETRYZOWANE
row_spec(nrow(Tabela), bold = T ,background = "#E3E3E3") %>% add_caption(name = "TOTAL RESULT ", position = "top") %>%
add_caption(name = "Tabela kontynuowana", position = "bottom")


zen <-gsub("(\\b[0-9]{4,15}\\b)","\\\\numprint{\\1}",zen)

zen


```

## TOTAL RESULT (YTD)

```{r MAINTOTdsdALYTD, echo=FALSE}
Tablica_X              <- CreateTable(MainTotalYTD,nazwa_tabeli = "MainTotalYTD")
Tabela1                <- Tablica_X[[1]]
Wiersze_do_boldowania1 <- Tablica_X[[2]]


# Tabela1[,2:17] <- lapply(Tabela1[,2:17], function(x) {
# cell_spec(x,
# color = ifelse(x<0,"#C815E0","black"))
# })
# 
# tbl <- tibble(test=c("A","B","C"), 
# 
#               
#                             link=c("someurl1", "someurl2", "someurl3"))
# 
# tbl %>% 
#   mutate(tbl$test[1] = paste0("\\href{http://", link, "}{", test, "}")) %>%
#   kable("latex", escape = FALSE, booktabs = TRUE) %>%
#   kable_styling(bootstrap_options = c("hover", "condensed")) 



```
